---
title: "linear model from Web"
author: "Benjamin Hardani"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS



### scatterplot

```{r}
plot(SIMS~ARM,data=data)
lmr=lm(SIMS~ARM, data = data)
abline(lmr)
```
The scatter plot has a positive line that does an ok job at predicting the strength needed for the workers.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The number coresponds with the graph in showing the correlation

### Inferential  (Build model.1)

```{r}
summary(lmr)
newdata=c(GRIP=94,ARM=88)
```
p-value is .00000000000000022 with an adjusted r squared of 0.467

#### Predict at target point

```{r}
predictSIM=predict.lm(lmr,newdata=data.frame(GRIP=94,ARM=88))
print(predictSIM)
```
Predicted accuracy of plot,seems positive.

#### scatterplot with model fit
  
```{r}
plot(lmr)
```
  The majority of the graphs seem to be a positive increasing slope and many are almost horizontal.

## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
YUR=lm(SIMS~GRIP, data = data)
abline(lmr)
```
The scatter plot has a positive line that does a worse job at predicting the strength needed for the workers. The original plot was better.


### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
The number coresponds with the graph in showing the correlation

### Inferential  (Build model.2)
  
```{r}
summary(YUR)
newdata=c(GRIP=94,ARM=88)
```
p-value is .00000000000000022 with an adjusted r squared of 0.4053


#### predict model.2 at target point

```{r}
predictSIM=predict.lm(YUR,newdata=data.frame(GRIP=94,ARM=88))
print(predictSIM)
```
Predicted accuracy of plot,seems positive and is better then previous model.

#### now add the model fit to our plot for model.2
  
```{r}
plot(YUR)
```
  The majority of the graphs seem to be a positive increasing slope and many are almost horizontal and do a better job of predicting outcomes.


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

````{r}
data2=lm(SIMS~ARM+GRIP,data=data)
summary(data2)
```
p-value is .00000000000000022 with an adjusted r squared of 0.5358 and a multiple r squared of 0.5422

  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  
```{r}
predict.lm(data2,newdata=data.frame(GRIP=94,ARM=88))
```
The number coresponds with the graph in showing the correlation

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
```{r}
anova(lmr,data2)
```


### Model.2 vs Model.3

```{r}
anova(YUR,data2)
```

## Informally compare Model.1 with model.2
Model 2 seems to be more accurate because if the higher decimal,4.994e-06 compared to 1.495e-09.
